---
title: "linreg_vignette"
description: >
  How to use linreg to fit linear regression models
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
```

## Introduction

In this vignette, we demonstrate how to use the `linreg()` function to fit a linear regression model. As an example, we will use the `airquality` dataset. The `airquality` dataset is comprised of 153 observations and 6 variables including:

-   Ozone (ppb)
-   Solar Radiation (lang)
-   Wind (mph)
-   Temp (F)
-   Month (1-12)
-   Day of Month (1-31)

## Using `linreg()` to fit model

Suppose we want to fit a linear regression model to find the association between temperature (outcome) and wind (covariate). Additionally, we want to adjust for Ozone and Month.

The `linreg(formula,data)` function requires inputs of formula and data which is based off of the `lm()` function in base R. For our example, the formula would be `Temp~Wind+Ozone+Month based on the variable names in the dataset.

```{r}

```







