---
title: "linreg_vignette"
description: >
  How to use linreg to fit linear regression models
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
library(bench)
```

## Introduction

In this vignette, we demonstrate how to use the `linreg()` function to fit a linear regression model. As an example, we will use the `airquality` dataset. The `airquality` dataset is comprised of 153 observations and 6 variables including:

-   Ozone (ppb)
-   Solar Radiation (lang)
-   Wind (mph)
-   Temp (F)
-   Month (1-12)
-   Day of Month (1-31)

## Using `linreg()` to fit model

Suppose we want to fit a linear regression model to find the association between temperature (outcome) and wind (covariate). Additionally, we want to adjust for Ozone and Month.

The `linreg(formula,data)` function requires inputs of formula and data which is based off of the `lm()` function in base R. For our example, the formula would be `Temp~Wind+Ozone+Month` based on the variable names in the dataset and data would be `airquality`.

```{r, message = FALSE}
linreg(Temp~Wind+Month+Ozone,airquality)
```

The `linreg()` function outputs all quantities of the function unlike the `lm()` function in base R. All components that are shown when the `lm()` function is called are shown near the top of the `linreg()` function. It is also possible to subset a specific quantity similar to the `lm()` function.

To select only the coefficients in `linreg()` output, we use the `$` to subset a specific quanitity.

```{r, message = FALSE}
#method using subset directly after function
linreg(Temp~Wind+Month+Ozone,airquality)$coefficients

#method assigning model to variable
model = linreg(Temp~Wind+Month+Ozone,airquality)
model$coefficients

```

## Using `linreg_sum()` to obtain summary of model

Using the same example above, suppose we want to obtain a summary of our linear regression model with more statistical details. The `linreg_sum()` function requires the same inputs of `linreg()`.

```{r, message=FALSE}
linreg_sum(Temp~Wind+Month+Ozone,airquality)
```

Similar to `linreg()`, the `linreg_sum()` also outputs all the quantities of the function. All outputs are that are shown in the output of `summary(lm({model}))` are included in the `linreg_sum()` function. You can also subset specific quantities you're looking for.

```{r, message=FALSE}
linreg_sum(Temp~Wind+Month+Ozone,airquality)$r.squared
```


## Comparing `linreg()` to `lm()`

To compare the correctness of the `linreg()` function to the original `lm()` function, we can use the `all.equal()` function. To demonstrate this, we will continue using the `airquality` dataset.

```{r, message=FALSE}
linreg_test = linreg(Temp~Wind+Month+Ozone,airquality)
lm_test = lm(Temp~Wind+Month+Ozone,airquality)
all.equal(linreg_test$coefficients,lm_test$coefficients)
all.equal(linreg_test$residuals,lm_test$residuals)
all.equal(linreg_test$rank,lm_test$rank)
all.equal(linreg_test$fitted.values,lm_test$fitted.values)
all.equal(linreg_test$df.residual,lm_test$df.residual)
all.equal(linreg_test$terms,lm_test$terms)
```

To compare the efficiency of `linreg()` and the `lm()` functions, we can use the `bench::mark()` function.

```{r}
bench::mark(linreg(Temp~Wind+Month+Ozone, airquality), lm(Temp~Wind+Month+Ozone,airquality), check = FALSE)
```












